\bf On Devon Allen's Disqualification at the 2022 World Track and Field Championships

### 2024-11-25 Manuscript/manuscript.tex
responded to Prof Yan and Prof Schifano's comments

\jy{Owen, are there names from 100-m dash?}
To compare RTs at the 2022 World Championships with those
recorded at national competitions, we constructed a dataset of athletes
who competed in both settings. Initially, we examined data from four
United States athletes---Trey Cunningham, Daniel Roberts, Grant
Holloway, and Devon Allen---who participated in both the United States
Track and Field Championships and the World Championships. Each athlete
recorded faster RTs in all World Championships races compared
to their performances at the national-level event. However, this small
sample size was insufficient for meaningful statistical analysis. To
expand the dataset, we included RTs from additional national
competitions held between May and July 2022 across various countries.
Compiling this data was challenging, as RTs were not centrally
located and often required searching country-specific websites, with many
results recorded in native languages.

@@

\jy{Could you do a pooled analysis since there is no gender difference
  and event differece in the supplement?}

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{RankScatterPlots}
  \caption{RTs for athletes who competed at the 2022 World Championships
	and at another championship (2022 national, 2019 World, or 2023 World) at which
	they competed. On the horizontal
  axis below each graph "H", "S", and "F" refer to the heats, semifinals, and
  finals respectively. Please note that in the last row the 2022 times are to
  the right of the 2023 times.
	\eds{Please check my edited caption; also, I suggest rearranging the rows to
	use the same ordering as the data was described: put national vs international
	in first row, 2019 vs 2022 in second row, and 2022 vs 2023 in third row}
	}
  \label{fig:RankScatterplots}
\end{figure}

@@

\eds{I also think we need to comment on the men and women's data. But within row
of the figure, don't the distributions appear similar?  If that is so, would a
reviewer ask why we didn't pool the data for men and women?}
\jy{Let's put the pooled analysis in the supplement.}

@@

\jy{have the numbers in this paragraph been updated with the
  additional 100-dash data?}
The data is summarized in Figure~\ref{fig:Boxplot}, which presents a
sequence of boxplots of RTs from 1999 to 2023. It is evident
that RTs in 2022 were notably faster, with a median reaction
time of 0.129 seconds compared to the 0.156 seconds observed in earlier
studies, such as \citet{brosnan2017effects} for data spanning 1999 to 2014.
Figure~\ref{fig:Boxplot} also highlights year-to-year variability in
RTs, likely influenced by changes in the championship venue
and environmental conditions such as humidity, precipitation, and
elevation. Furthermore, advancements in technology and alterations to
false start rules during the study period may have played a role in these
variations \citep{willwacher2013novel}.

@@

\jy{Are these numbers correct? I modified with the gg3b in gg.R}

\begin{table}
  \centering
  \caption{Estimated fixed-effect parameters with standard errors in
    parentheses and estimated variance of the random effects from the
    fitted GG distribution with venue level random
    effects in $\mu$ and heat level random effects in $\sigma$ in
    Models~\eqref{eq:gg}--\eqref{eq:sigma}.}
  \label{tab:ggfit}
  \begin{tabular}{c c c c c c}
    \toprule
    Data set & $\beta_0$ & $\gamma_0$ & $\nu$ & $\sigma_v$ & $\sigma_h$ \\
    \midrule
    Excluding 2022 & $-$1.910 (0.005)  & $-$2.200 (0.025) & $-$1.177 (0.442) & 0.043 & 0.326 \\
    Including 2022 & $-$1.910 & $-$2.200 & $-$1.178 & 0.058 & 0.320 \\
    \bottomrule
  \end{tabular}
\end{table}

@@

\jy{Could you also test sensitivity for excluding the positive but
  fault RTs?}

>>>>

\jy{Owen, are there names from 100-m dash?}
\of{Yes, there were four US athletes in the 100m dash that we have data on.
Marvin Bracy, Fred Kerley, Travyon Bromwell, and Christian Coleman.  All of whom
recorded their slowest times at the US Track and Field Championship.}
To compare RTs at the 2022 World Championships with those
recorded at national competitions, we constructed a dataset of athletes
who competed in both settings. Initially, we examined data from four
United States athletes---Trey Cunningham, Daniel Roberts, Grant
Holloway, and Devon Allen---who participated in both the United States
Track and Field Championships and the World Championships. Each athlete
recorded faster RTs in all World Championships races compared
to their performances at the national-level event. However, this small
sample size was insufficient for meaningful statistical analysis. To
expand the dataset, we included RTs from additional national
competitions held between May and July 2022 across various countries.
Compiling this data was challenging, as RTs were not centrally
located and often required searching country-specific websites, with many
results recorded in native languages.

@@

\jy{Could you do a pooled analysis since there is no gender difference
  and event differece in the supplement?}
\of{Asked you about this in an email.}

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{RankScatterPlots}
  \caption{RTs for athletes who competed at the 2022 World Championships
	and at another championship (2022 national, 2019 World, or 2023 World) at which
	they competed. On the horizontal
  axis below each graph "H", "S", and "F" refer to the heats, semifinals, and
  finals respectively. Please note that in the last row the 2022 times are to
  the right of the 2023 times.
	\eds{Please check my edited caption; also, I suggest rearranging the rows to
	use the same ordering as the data was described: put national vs international
	in first row, 2019 vs 2022 in second row, and 2022 vs 2023 in third row}
	}
  \of{I agree and I updated it. I think it looks good now.}
  \label{fig:RankScatterplots}
\end{figure}

@@

\eds{I also think we need to comment on the men and women's data. But within row
of the figure, don't the distributions appear similar?  If that is so, would a
reviewer ask why we didn't pool the data for men and women?}
\jy{Let's put the pooled analysis in the supplement.}
\of{Yes I believe the distributions are similar but I think we cover why we don't
pool by citing the papers that suggest differences in men and women's times.}

@@

\jy{have the numbers in this paragraph been updated with the
  additional 100-dash data?}
  \of{Funny enough the median reaction time remained exactly the same.}
The data is summarized in Figure~\ref{fig:Boxplot}, which presents a
sequence of boxplots of RTs from 1999 to 2023. It is evident
that RTs in 2022 were notably faster, with a median reaction
time of 0.129 seconds compared to the 0.156 seconds observed in earlier
studies, such as \citet{brosnan2017effects} for data spanning 1999 to 2014.
Figure~\ref{fig:Boxplot} also highlights year-to-year variability in
RTs, likely influenced by changes in the championship venue
and environmental conditions such as humidity, precipitation, and
elevation. Furthermore, advancements in technology and alterations to
false start rules during the study period may have played a role in these
variations \citep{willwacher2013novel}.

@@

\jy{Are these numbers correct? I modified with the gg3b in gg.R}
\of{Yes I agree with your numbers and have included the ones for the other model}

\of{I moved the table down because in the pdf it was appearing in the rank
section.} 
\of{I think it's confusing that sigma appears as a parameter of the model
and we use it as the standard deviation of the heat effect which appears in the
sigma parameter. I don't know much about statistical nomenclature in papers, is
this common?}

\begin{table}
  \centering
  \caption{Estimated fixed-effect parameters with standard errors in
    parentheses and estimated variance of the random effects from the
    fitted GG distribution with venue level random
    effects in $\mu$ and heat level random effects in $\sigma$ in
    Models~\eqref{eq:gg}--\eqref{eq:sigma}.}
  \label{tab:ggfit}
  \begin{tabular}{c c c c c c}
    \toprule
    Data set & $\beta_0$ & $\gamma_0$ & $\nu$ & $\sigma_v$ & $\sigma_h$ \\
    \midrule
    Excluding 2022 & $-$1.910 (0.005) & $-$2.200 (0.025) & $-$1.177 (0.442) & 0.043 & 0.326 \\
    Including 2022 & $-$1.910 (0.005) & $-$2.200 (0.027) & $-$1.178 (0.447) & 0.058 & 0.320 \\
    \bottomrule
  \end{tabular}
\end{table}

@@

\jy{Could you also test sensitivity for excluding the positive but
  fault RTs?}
\of{Yes I explained the code is at the bottom of gg.R and ran code without 2022: for 0.1 the
probability is $1.97\cdot10^{-3}$ versus $2.76\cdot10^{-3}$. For 0.09: the
probability is $3.53\cdot10^{-4}$ versus $4.95\cdot10^{-4}$. For 0.08: the
probability is $4.93\cdot10^{-5}$ versus $6.84\cdot10^{-5}$. I assume we want
to report these in the supplemental?}
